\section{Introduction}

The widespread deployment of wireless technologies such as Wi-Fi and Wi-Max 
in today's networks has resulted in the emergence of an increasing number 
of mobile hand-held devices such as mobile phones and PDAs capable of data 
processing and communication. It is expected that the number of such devices 
will only increase in the future. However, Voice-over IP (VoIP) and other 
real-time streaming applications pose a serious challenge in achieving true 
mobility in Wi-Fi networks. This is partially because of the high handoff 
latencies~\cite{956990} and the resultant severe data loss experienced by mobile users 
while moving from one access point (AP) to another. Our goal in this work 
is to develop a system to eliminate handoff latency and data loss during 
handoff by exploiting the potential of multiple radios in mobile devices. 
We develop a novel hand-over scheme, {\bf \sys{}}, that achieves seamless mobility 
without data loss. 
%It is essentially a combination of a client-side program 
%and a NOX-based mobility manager that realizes seamless mobile handoff over 
%Open-Flow enabled Wi-Fi networks.

Previous works that have proposed the idea of using two radios~\cite{brik}, achieve only
the partial goal of zero handoff latency. However, because of a lack of
complete control over flows within the network, they fail to provide a solution to
eliminate the loss of downstream packets during handoff. OpenFlow~\cite{openflow} provides us with 
this capability, and we exploit it to achieve lossless hand-over.

